Functional Pearl: Short and Mechanized Logical Relation for Dependent Type Theories

### 2024-02-27 paper/paper.tex
compress typing figure

\yl{Need to fix the de bruijn text}
We adapt from \citet{autosubst2} notation for simultaneous renaming,
substitution, and other auxiliary definitions used in our paper, summarized in
Figure~\ref{fig:auxdef}. We need these definitions to specify the reduction
and typing relations for \lang{}. The metavariable $[[rho]]$ represents
substitutions, which are mappings from de Bruijn indices to terms.  One
example of a substitution is the function $\ottkw{id}_{tm}$,\scw{Can we just 
call this \ottkw{id} now?} the identity
substitution that maps each index to the corresponding term variable.  % The
% $...$ substitution is more general and adds $[[n]]$ to the index
% before injecting it as a term.
The extension operation, $[[(rho .: x -> a)]]$,
allows us to update the substitution $[[rho]]$ to map the variable
$[[x]]$ to $[[a]]$ rather than $[[rho x]]$.

@@

\yl{Explain why iterated substitution is not good enough}

@@

\begin{figure}[h]
\begin{minipage}{0.9\textwidth}
\drules[Ctx]{$[[ |- G]]$}{Context Well-Formedness}{Empty, Cons}
\drules[T]{$[[G |-  a : A]]$}{Typing}{Var, Set, Pi, Abs, App, Conv,
  Eq, Refl, J, If, Bool, True, False, Void}
\end{minipage}
\caption{Syntactic typing for \lang}
\label{fig:typing}
\end{figure}

>>>>

\yl{Need to fix the de bruijn text}
We adapt from \citet{autosubst2} notation for simultaneous renaming,
substitution, and other auxiliary definitions used in our paper, summarized in
Figure~\ref{fig:auxdef}. We need these definitions to specify the reduction
and typing relations for \lang{}. The metavariable $[[rho]]$ represents
substitutions, which are mappings from de Bruijn indices to terms.  One
example of a substitution is the function $\ottkw{id}_{tm}$,\scw{Can we just 
call this $\ottkw{id}$ now?} the identity
substitution that maps each index to the corresponding term variable.  % The
% $...$ substitution is more general and adds $[[n]]$ to the index
% before injecting it as a term.
The extension operation, $[[(rho .: x -> a)]]$,
allows us to update the substitution $[[rho]]$ to map the variable
$[[x]]$ to $[[a]]$ rather than $[[rho x]]$.

@@

\yl{Explain why iterated substitution is not good enough}
\scw{resolved below, right?}

@@

\begin{figure}[h]
\begin{minipage}{0.9\textwidth}
\drules[Ctx]{$[[ |- G]]$}{Context Well-Formedness}{Empty, Cons}
\drules[T]{$[[G |-  a : A]]$}{Typing}{Var, Set, Pi, Abs, App, Conv,
 Void, Bool, True, False}
\[ \drule[width=5in]{T-If}\]
\[ \drule[width=3in]{T-Eq} \qquad \drule{T-Refl} \]
\[ \drule[width=4in]{T-J} \]
\end{minipage}
\caption{Syntactic typing for \lang}
\label{fig:typing}
\end{figure}
